More on the Slavnov products of spin chains, KP hierarchy tau and Baker-Akhiezer functions

### 2025-05-21 draft.tex
start ba function

In the previous section, we discussed the limit in which the
parameters \(\bm{z}\) approach the Bethe roots \(\bm{v}\).  We now
consider a different limit, where all variables in the set \(\bm{z}\)
tend to a single variable -- that is, \(z_k\to z_1\) for \(k=2,\dots,
n\).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Examples}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Let us now consider the cases \(n=2, 3\) (the case \(n=1\) is trivial)
to gain some understanding of the problem.

\subsection{n=2} In this case, we have \(\mathcal{Y}_j\) for \(j=1,2\) and two Bethe roots
\(\bm{v} = (v_1, v_2)\). Moreover, we have the two sets \(\bm{v}_1 =
\{v_2\}\) and \(\bm{v}_2 = \{v_1\}\). From (\ref{eq:y-functions}), we have
\begin{subequations}
\begin{equation}
  \begin{split}
    \mathcal{Y}_j(z) =
    \alpha_0(z) \sigma_0^{(1)}(\bm{v}_j) +  
    \alpha_1(z)( \sigma_1^{(1)}(\bm{v}_j) + z \sigma_0^{(1)}(\bm{v}_j)) +
    \alpha_2(z) z \sigma_1^{(1)}(\bm{v}_j) \; , 
  \end{split}
\end{equation}
finally, the explicit formulas for the elementary symmetric polynomials are \(\sigma_0^{(1)}(x) =1\)
and \(\sigma_1^{(1)}(x) = x\).

Therefore
\begin{equation}
  \begin{split}
    \mathcal{Y}_1(z) & = \alpha_0(z) + z \alpha_1(z)  + v_2 \left( \alpha_1(z) + z \alpha_2(z) \right) \\ 
    \mathcal{Y}_2(z) & = \alpha_0(z) + z \alpha_1(z)  + v_1 \left( \alpha_1(z) + z \alpha_2(z) \right) ; .
  \end{split}
\end{equation}
Consequently, we find
\begin{equation}
\begin{split}
  \bm{\tau}(z_1, z_2; v_1 , v_2)
  & = \frac{1}{z_2 - z_1} \left(\frac{\mathcal{Y}_1(z_1) \mathcal{Y}_2(z_2)}{(z_1 - v_1)(z_2 - v_2)} - 
  \frac{\mathcal{Y}_1(z_2) \mathcal{Y}_2(z_1)}{(z_1 - v_2)(z_2 - v_1)} \right)\\
  & = \frac{1}{z_2 - z_1}
  \left(
  \frac{\mathcal{Y}_1(z_1)}{(z_1 - v_1)} \widetilde{\bm{\tau}}_1(z_2, v_1, v_2) - 
  \frac{\mathcal{Y}_2(z_1)}{(z_1 - v_2)} \widetilde{\bm{\tau}}_2(z_2, v_1, v_2) \right)
\end{split}
\end{equation}
where 
\begin{equation}
 \widetilde{\bm{\tau}}_1(z_2, v_1, v_2) = \frac{\mathcal{Y}_2(z_2)}{(z_2 - v_2)} \quad \textrm{and}  \qquad 
 \widetilde{\bm{\tau}}_2(z_2, v_1, v_2) = \frac{\mathcal{Y}_1(z_2)}{(z_2 - v_1)}  \; .
\end{equation}
\end{subequations}
From this expression, it is easy to extract the residues of \(z_1\)
about one of the Bethe roots.

It is easy to see that the homogeneous limit, that is \(z_2 \to z_1\equiv
w\) gives
\begin{equation}
  \bm{\tau}(w; v_1 , v_2) =
  \frac{1}{(w- v_1)(w- v_2)}\mathcal{W}[\mathcal{Y}_1, \mathcal{Y}_2](w)\; , 
\end{equation}
It is also elementary to see that the functions \(\{\mathcal{Y}_1,
\mathcal{Y}_2\}\) are linearly independent as long as \(v_2 \neq
v_1\), what is guaranteed by the hypothesis that the Bethe roots are
different.

\subsection{n=3} Now we have \(\mathcal{Y}_j\) for \(j=1,2,3\) and three Bethe roots
\(\bm{v} = (v_1, v_2, v_3)\). Moreover, we have the sets \(\bm{v}_1 = (v_2, v_3)\), \(\bm{v}_2 = (v_1, v_3)\)
and \(\bm{v}_3 = (v_1, v_2)\). Then, it is easy to see that
\begin{equation}
\begin{split}
  \mathcal{Y}_j(z)
  & = (\alpha_0(z) + z \alpha_1(z))\sigma_0^{(2)}(\bm{v}_j)   + (\alpha_1(z) + z \alpha_2(z))\sigma_1^{(2)}(\bm{v}_j)  + \\
  & \quad + (\alpha_2(z) + z \alpha_3(z))\sigma_2^{(2)}(\bm{v}_j) \; ,
\end{split}
\end{equation}
with the explicit expressions 
\begin{equation}
  \sigma_0^{(2)}(x, y) = 1\; ,\qquad 
  \sigma_1^{(2)}(x, y) = x + y\; ,\qquad 
  \sigma_2^{(2)}(x, y) = x^2 + xy  + y^2\; . 
\end{equation}

Then, we have
\begin{subequations}
\begin{equation}
  \begin{split}
    \bm{\tau} & (z_1, z_2, z_3 ; v_1 , v_2, v_3)  =
    \frac{1}{(z_2 - z_1)(z_3 - z_1)(z_3 - z_2)}\times \\
    & \times \left[
      \frac{\mathcal{Y}_1(z_1)}{z_1 - v_1}
        \det\begin{bmatrix}
        \frac{\mathcal{Y}_2(z_2)}{(z_2 - v_2)} & \frac{\mathcal{Y}_2(z_3)}{(z_3 - v_2)}\\
        \frac{\mathcal{Y}_3(z_2)}{(z_2 - v_3)} & \frac{\mathcal{Y}_3(z_3)}{(z_3 - v_3)}
        \end{bmatrix}
        -  
      \frac{\mathcal{Y}_2(z_1)}{z_1 - v_2}
        \det\begin{bmatrix}
        \frac{\mathcal{Y}_1(z_2)}{(z_2 - v_1)} & \frac{\mathcal{Y}_1(z_3)}{(z_3 - v_1)}\\
        \frac{\mathcal{Y}_3(z_2)}{(z_2 - v_3)} & \frac{\mathcal{Y}_3(z_3)}{(z_3 - v_3)}
        \end{bmatrix} \right.\\
        & \qquad + \left.
      \frac{\mathcal{Y}_3(z_1)}{z_1 - v_2}
        \det\begin{bmatrix}
        \frac{\mathcal{Y}_1(z_2)}{(z_2 - v_1)} & \frac{\mathcal{Y}_1(z_3)}{(z_3 - v_1)}\\
        \frac{\mathcal{Y}_2(z_2)}{(z_2 - v_2)} & \frac{\mathcal{Y}_2(z_3)}{(z_3 - v_2)}
        \end{bmatrix} 
  \right] \; .
  \end{split}
\end{equation}
We organize this expression as
\begin{equation}
  \begin{split}
    \bm{\tau} (z_1, z_2, z_3 ; v_1 , v_2, v_3)  & =
    \frac{1}{(z_2 - z_1)(z_3 - z_1)}
    \left[
      \frac{\mathcal{Y}_1(z_1)}{z_1 - v_1}
      \left(
      \frac{1}{(z_3 - z_2)}
        \det\begin{bmatrix}
        \frac{\mathcal{Y}_2(z_2)}{(z_2 - v_2)} & \frac{\mathcal{Y}_2(z_3)}{(z_3 - v_2)}\\
        \frac{\mathcal{Y}_3(z_2)}{(z_2 - v_3)} & \frac{\mathcal{Y}_3(z_3)}{(z_3 - v_3)}
        \end{bmatrix}
        \right) - \right. \\
        & - 
      \frac{\mathcal{Y}_2(z_1)}{z_1 - v_2}
      \left(
      \frac{1}{(z_3 - z_2)}
        \det\begin{bmatrix}
        \frac{\mathcal{Y}_1(z_2)}{(z_2 - v_1)} & \frac{\mathcal{Y}_1(z_3)}{(z_3 - v_1)}\\
        \frac{\mathcal{Y}_3(z_2)}{(z_2 - v_3)} & \frac{\mathcal{Y}_3(z_3)}{(z_3 - v_3)}
        \end{bmatrix} \right) \\
        & +
        \left.
      \frac{\mathcal{Y}_3(z_1)}{z_1 - v_2}
      \left(
      \frac{1}{(z_3 - z_2)}
        \det\begin{bmatrix}
        \frac{\mathcal{Y}_1(z_2)}{(z_2 - v_1)} & \frac{\mathcal{Y}_1(z_3)}{(z_3 - v_1)}\\
        \frac{\mathcal{Y}_2(z_2)}{(z_2 - v_2)} & \frac{\mathcal{Y}_2(z_3)}{(z_3 - v_2)}
        \end{bmatrix} 
        \right)
  \right]\; .
  \end{split}
\end{equation}
\end{subequations}

Finally, we conclude that that basis tau functions are
\begin{subequations}
  \begin{equation}
	\tilde{\bm{\tau}}_1(\bm{z}_1) = \frac{1}{(z_3 - z_2)} 
        \det\begin{bmatrix}
        \frac{\mathcal{Y}_2(z_2)}{(z_2 - v_2)} & \frac{\mathcal{Y}_2(z_3)}{(z_3 - v_2)}\\
        \frac{\mathcal{Y}_3(z_2)}{(z_2 - v_3)} & \frac{\mathcal{Y}_3(z_3)}{(z_3 - v_3)}
        \end{bmatrix} 
  \end{equation}
  \begin{equation}
	\tilde{\bm{\tau}}_2(\bm{z}_1) = \frac{1}{(z_3 - z_2)} 
        \det\begin{bmatrix}
        \frac{\mathcal{Y}_1(z_2)}{(z_2 - v_1)} & \frac{\mathcal{Y}_1(z_3)}{(z_3 - v_1)}\\
        \frac{\mathcal{Y}_3(z_2)}{(z_2 - v_3)} & \frac{\mathcal{Y}_3(z_3)}{(z_3 - v_3)}
       \end{bmatrix}
  \end{equation}
  \begin{equation}
	\tilde{\bm{\tau}}_3(\bm{z}_1) = \frac{1}{(z_3 - z_2)} 
        \det\begin{bmatrix}
        \frac{\mathcal{Y}_1(z_2)}{(z_2 - v_1)} & \frac{\mathcal{Y}_1(z_3)}{(z_3 - v_1)}\\
        \frac{\mathcal{Y}_2(z_2)}{(z_2 - v_2)} & \frac{\mathcal{Y}_2(z_3)}{(z_3 - v_2)}
        \end{bmatrix} \; .
  \end{equation}
\end{subequations}

With these expressions, we can consider the case where \(z_1, z_2 z_3
\to w\). Consider first the case \(z_3 \to z_2 = w\), then  
we know that 
\begin{equation}
  \begin{split}
  \tilde{\bm{\tau}}_1(w; v_1 , v_2, v_3) & = \frac{1}{(w - v_2)(w - v_3)}\mathcal{W}[\mathcal{Y}_2, \mathcal{Y}_3](w)\\
  \tilde{\bm{\tau}}_2(w; v_1 , v_2, v_3) & = \frac{1}{(w - v_2)(w - v_3)}\mathcal{W}[\mathcal{Y}_1, \mathcal{Y}_3](w)\\
  \tilde{\bm{\tau}}_3(w; v_1 , v_2, v_3) & = \frac{1}{(w - v_1)(w - v_2)}\mathcal{W}[\mathcal{Y}_1, \mathcal{Y}_2](w)
  \; .
  \end{split}
\end{equation}
and now, it is easy to see that if we also take the limit \(z_1\to w\), we have
\begin{equation}
  \bm{\tau}(w; v_1 , v_2, v_3) = 
  \frac{1}{(w - v_1)(w - v_2)(w - v_3)} \mathcal{W}[\mathcal{Y}_1, \mathcal{Y}_2, \mathcal{Y}_3](w)\; .
\end{equation}

Of course we can keep the calculations for other cases, but now it is obvious that
this explicit analysis become cumbersome very early. It also explains why we
keep our analysis restricted to the Rational cases.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Baker-Akhiezer function}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

This section deals with some properties of the Baker-Akhiezer
functions associated to the tau functions we found above.  Many
aspects of these functions deserve a thorough examination, but here we
investigagte just the most immediate aspects.

@@

We now want to write the Slavnov products we defined above in terms of
the following coordinates
\begin{equation}
  t_p = \frac{1}{p}\sum_{j=1}^n z_j^p\; ,
\end{equation}
the so called Miwa coordinates.

We define
\begin{equation}
  \xi(\bm{t}, \lambda) = \sum_{p=1}^\infty t_p \lambda^p\; , 
\end{equation}
where \(\lambda\) is a complex parameter. Therefore
\begin{equation}
  \begin{split}
    e^{\xi(\bm{t}, \lambda)} & = \exp\left( \sum_{p=1}^\infty t_p \lambda^p \right)
    = \exp\left( \sum_{p=1}^\infty \sum_{j=1}^n \frac{1}{p} z^p \lambda^p \right) \\
    & = \exp\left( \sum_{j=1}^n \sum_{p=1}^\infty  \frac{1}{p} z_j^p \lambda^p \right)
    = \exp\left( - \sum_{j=1}^n \ln( 1 -  z_j \lambda ) \right) \\
    & =  \prod_{j=1}^n \frac{1}{1 -  z_j \lambda} \; .
  \end{split}
\end{equation}
It is easy to see that these functions have simple poles at \( \lambda
= z_j^{-1}\).

Let us now establish an important result,
see ~\cite{Araujo:2021ghu} and references therein. 
\begin{proposition}
The tau function~(\ref{eq:slav-tau-function}) admits the following integral
representation 
\begin{subequations}
\begin{equation}
  \label{eq:tau-function-miwa}
  \bm{\tau}(\bm{t}, \bm{v}) =
    \det_{j,k}\left(
    \oint_{\gamma_k} \frac{d w}{2\pi i} e^{\xi(\bm{t}, w^{-1})} \frac{w^{-j}\mathcal{Y}_k(w)}{w - v_k} \right)\; ,
\end{equation}
where 
\begin{equation}
  \xi(\bm{t}, w^{-1}) = \sum_{p=1}^\infty t_p w^{-p} \quad \Leftrightarrow \quad
  \xi(\bm{z}, w^{-1}) = w^n \prod_{j=1}^n (w - z_j)^{-1} \; . 
\end{equation}
In the above integral, we consider that integration curve \(\gamma_k\)
encloses all poles except the Bethe root \(v_k\).
\end{subequations}
\end{proposition}

\paragraph{\textbf{\emph{Proof}}}
In terms of the \(z\)-coordinates, the tau functions becomes
\begin{equation}
  \label{eq:tau-function}
  \bm{\tau}(\bm{z}, \bm{v}) =
    \det_{j,k}\left(
    \oint_{\gamma_k} \frac{d w}{2\pi i}
    \prod_{l=1}^n \frac{1}{w - z_l} \frac{w^{n-j}\mathcal{Y}_k(w)}{w - v_k} \right) \; . 
\end{equation}
Now, it is easy to see that \(w =0\) is not a pole.  All in all, the
integration curve \(\gamma_k\) encloses points \(\{z_j\}_{j=1}^n\).

>>>>

In the previous section, we discussed the limit in which the
parameters \(\bm{z}\) approach the Bethe roots \(\bm{v}\).  We now
consider a different limit, where all variables in the set \(\bm{z}\)
tend to a single variable -- that is, \(z_k\to z_1\) for \(k=2,\dots,
n\). The analysis follows the ideas of~\cite{Izergin:1991rs}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Examples}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Let us now consider the cases \(n = 2\) and \(n = 3\) to gain further
insight into the problem.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Case n=2}
In this case, we have \(\mathcal{Y}_j\) for \(j = 1, 2\) and two Bethe
roots \(\bm{v} = (v_1, v_2)\). Moreover, we define the two sets
\(\bm{v}_1 = \{v_2\}\) and \(\bm{v}_2 = \{v_1\}\). From
equation~(\ref{eq:y-functions}), we have
\begin{subequations}
\begin{equation}
  \begin{split}
    \mathcal{Y}_j(z) =
    \alpha_0(z) \sigma_0^{(1)}(\bm{v}_j) +  
    \alpha_1(z)( \sigma_1^{(1)}(\bm{v}_j) + z \sigma_0^{(1)}(\bm{v}_j)) +
    \alpha_2(z) z \sigma_1^{(1)}(\bm{v}_j) \; . 
  \end{split}
\end{equation}
Furthermore, the explicit formulas for the elementary symmetric
polynomials are \(\sigma_0^{(1)}(x) = 1\) and \(\sigma_1^{(1)}(x) =
x\). Therefore
\begin{equation}
  \begin{split}
    \mathcal{Y}_1(z) & = \alpha_0(z) + z \alpha_1(z)  + v_2 \left( \alpha_1(z) + z \alpha_2(z) \right) \\ 
    \mathcal{Y}_2(z) & = \alpha_0(z) + z \alpha_1(z)  + v_1 \left( \alpha_1(z) + z \alpha_2(z) \right) \; .
  \end{split}
\end{equation}
Consequently, the normalized Slavnov product becomes
\begin{equation}
\begin{split}
  \bm{\tau}(z_1, z_2; v_1 , v_2)
  & = \frac{1}{z_2 - z_1} \left(\frac{\mathcal{Y}_1(z_1) \mathcal{Y}_2(z_2)}{(z_1 - v_1)(z_2 - v_2)} - 
  \frac{\mathcal{Y}_1(z_2) \mathcal{Y}_2(z_1)}{(z_1 - v_2)(z_2 - v_1)} \right)\\
  & = \frac{1}{z_2 - z_1}
  \left(
  \frac{\mathcal{Y}_1(z_1)}{(z_1 - v_1)} \widetilde{\bm{\tau}}_1(z_2, v_1, v_2) - 
  \frac{\mathcal{Y}_2(z_1)}{(z_1 - v_2)} \widetilde{\bm{\tau}}_2(z_2, v_1, v_2) \right)\; ,
\end{split}
\end{equation}
where 
\begin{equation}
 \widetilde{\bm{\tau}}_1(z_2, v_1, v_2) = \frac{\mathcal{Y}_2(z_2)}{(z_2 - v_2)} \quad \textrm{and}  \qquad 
 \widetilde{\bm{\tau}}_2(z_2, v_1, v_2) = \frac{\mathcal{Y}_1(z_2)}{(z_2 - v_1)}  \; .
\end{equation}
\end{subequations}

From this expression, it is easy to extract the residues of \(z_1\) at
one of the Bethe roots. It is also straightforward to see that the
homogeneous limit, that is, \(z_2 \to z_1 \equiv w\), yields
\begin{equation}
  \bm{\tau}(w; v_1 , v_2) =
  \frac{1}{(w- v_1)(w- v_2)}\mathcal{W}[\mathcal{Y}_1, \mathcal{Y}_2](w)\; . 
\end{equation}
It is also elementary to see that the functions \(\{\mathcal{Y}_1,
\mathcal{Y}_2\}\) are linearly independent as long as \(v_2 \neq
v_1\), which is guaranteed by the assumption that the Bethe roots are
distinct.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Case n=3}
Now we have \(\mathcal{Y}_j\) for \(j=1,2,3\), and three Bethe roots
\(\bm{v} = (v_1, v_2, v_3)\). Moreover, we define the sets \(\bm{v}_1
= (v_2, v_3)\), \(\bm{v}_2 = (v_1, v_3)\), and \(\bm{v}_3 = (v_1,
v_2)\). Then, it is easy to see that
\begin{equation}
\begin{split}
  \mathcal{Y}_j(z)
  & = (\alpha_0(z) + z \alpha_1(z))\sigma_0^{(2)}(\bm{v}_j)   + (\alpha_1(z) + z \alpha_2(z))\sigma_1^{(2)}(\bm{v}_j)  + \\
  & \quad + (\alpha_2(z) + z \alpha_3(z))\sigma_2^{(2)}(\bm{v}_j) \; ,
\end{split}
\end{equation}
with
\begin{equation}
  \sigma_0^{(2)}(x, y) = 1\; ,\qquad 
  \sigma_1^{(2)}(x, y) = x + y\; ,\qquad 
  \sigma_2^{(2)}(x, y) = x^2 + xy  + y^2\; . 
\end{equation}

Hence
\begin{subequations}
\begin{equation}
\begin{split}
\bm{\tau} & (z_1, z_2, z_3 ; v_1 , v_2, v_3)  =
\frac{1}{(z_2 - z_1)(z_3 - z_1)(z_3 - z_2)}\times \\
& \times \left[
    \frac{\mathcal{Y}_1(z_1)}{z_1 - v_1}
    \det\begin{bmatrix}
    \frac{\mathcal{Y}_2(z_2)}{(z_2 - v_2)} & \frac{\mathcal{Y}_2(z_3)}{(z_3 - v_2)}\\
    \frac{\mathcal{Y}_3(z_2)}{(z_2 - v_3)} & \frac{\mathcal{Y}_3(z_3)}{(z_3 - v_3)}
    \end{bmatrix}
    -  
    \frac{\mathcal{Y}_2(z_1)}{z_1 - v_2}
    \det\begin{bmatrix}
    \frac{\mathcal{Y}_1(z_2)}{(z_2 - v_1)} & \frac{\mathcal{Y}_1(z_3)}{(z_3 - v_1)}\\
    \frac{\mathcal{Y}_3(z_2)}{(z_2 - v_3)} & \frac{\mathcal{Y}_3(z_3)}{(z_3 - v_3)}
    \end{bmatrix} \right.\\
    & \qquad + \left.
    \frac{\mathcal{Y}_3(z_1)}{z_1 - v_2}
    \det\begin{bmatrix}
    \frac{\mathcal{Y}_1(z_2)}{(z_2 - v_1)} & \frac{\mathcal{Y}_1(z_3)}{(z_3 - v_1)}\\
    \frac{\mathcal{Y}_2(z_2)}{(z_2 - v_2)} & \frac{\mathcal{Y}_2(z_3)}{(z_3 - v_2)}
    \end{bmatrix} 
\right] \; .
\end{split}
\end{equation}
We reorganize this expression as follows:
\begin{equation}
\begin{split}
\bm{\tau} (z_1, z_2, z_3 ; v_1 , v_2, v_3)  & =
\frac{1}{(z_2 - z_1)(z_3 - z_1)}
\left[
    \frac{\mathcal{Y}_1(z_1)}{z_1 - v_1}
    \left(
    \frac{1}{(z_3 - z_2)}
    \det\begin{bmatrix}
    \frac{\mathcal{Y}_2(z_2)}{(z_2 - v_2)} & \frac{\mathcal{Y}_2(z_3)}{(z_3 - v_2)}\\
    \frac{\mathcal{Y}_3(z_2)}{(z_2 - v_3)} & \frac{\mathcal{Y}_3(z_3)}{(z_3 - v_3)}
    \end{bmatrix}
    \right) - \right. \\
    & - 
    \frac{\mathcal{Y}_2(z_1)}{z_1 - v_2}
    \left(
    \frac{1}{(z_3 - z_2)}
    \det\begin{bmatrix}
    \frac{\mathcal{Y}_1(z_2)}{(z_2 - v_1)} & \frac{\mathcal{Y}_1(z_3)}{(z_3 - v_1)}\\
    \frac{\mathcal{Y}_3(z_2)}{(z_2 - v_3)} & \frac{\mathcal{Y}_3(z_3)}{(z_3 - v_3)}
    \end{bmatrix} \right) \\
    & +
    \left.
    \frac{\mathcal{Y}_3(z_1)}{z_1 - v_2}
    \left(
    \frac{1}{(z_3 - z_2)}
    \det\begin{bmatrix}
    \frac{\mathcal{Y}_1(z_2)}{(z_2 - v_1)} & \frac{\mathcal{Y}_1(z_3)}{(z_3 - v_1)}\\
    \frac{\mathcal{Y}_2(z_2)}{(z_2 - v_2)} & \frac{\mathcal{Y}_2(z_3)}{(z_3 - v_2)}
    \end{bmatrix} 
    \right)
\right]\; .
\end{split}
\end{equation}
\end{subequations}

Finally, we conclude that the basis tau functions are
\begin{subequations}
  \begin{equation}
	\tilde{\bm{\tau}}_1(\bm{z}_1) = \frac{1}{(z_3 - z_2)} 
        \det\begin{bmatrix}
        \frac{\mathcal{Y}_2(z_2)}{(z_2 - v_2)} & \frac{\mathcal{Y}_2(z_3)}{(z_3 - v_2)}\\
        \frac{\mathcal{Y}_3(z_2)}{(z_2 - v_3)} & \frac{\mathcal{Y}_3(z_3)}{(z_3 - v_3)}
        \end{bmatrix} 
  \end{equation}
  \begin{equation}
	\tilde{\bm{\tau}}_2(\bm{z}_1) = \frac{1}{(z_3 - z_2)} 
        \det\begin{bmatrix}
        \frac{\mathcal{Y}_1(z_2)}{(z_2 - v_1)} & \frac{\mathcal{Y}_1(z_3)}{(z_3 - v_1)}\\
        \frac{\mathcal{Y}_3(z_2)}{(z_2 - v_3)} & \frac{\mathcal{Y}_3(z_3)}{(z_3 - v_3)}
       \end{bmatrix}
  \end{equation}
  \begin{equation}
	\tilde{\bm{\tau}}_3(\bm{z}_1) = \frac{1}{(z_3 - z_2)} 
        \det\begin{bmatrix}
        \frac{\mathcal{Y}_1(z_2)}{(z_2 - v_1)} & \frac{\mathcal{Y}_1(z_3)}{(z_3 - v_1)}\\
        \frac{\mathcal{Y}_2(z_2)}{(z_2 - v_2)} & \frac{\mathcal{Y}_2(z_3)}{(z_3 - v_2)}
        \end{bmatrix} \; . 
  \end{equation}
\end{subequations}

With these expressions, we can consider the homogeneous limit \(z_1,
z_2, z_3 \to w\). Consider first the case \(z_3 \to z_2 = w\), then we
know that
\begin{equation}
  \begin{split}
  \tilde{\bm{\tau}}_1(w; v_1 , v_2, v_3) & = \frac{1}{(w - v_2)(w - v_3)}\mathcal{W}[\mathcal{Y}_2, \mathcal{Y}_3](w)\\
  \tilde{\bm{\tau}}_2(w; v_1 , v_2, v_3) & = \frac{1}{(w - v_2)(w - v_3)}\mathcal{W}[\mathcal{Y}_1, \mathcal{Y}_3](w)\\
  \tilde{\bm{\tau}}_3(w; v_1 , v_2, v_3) & = \frac{1}{(w - v_1)(w - v_2)}\mathcal{W}[\mathcal{Y}_1, \mathcal{Y}_2](w)
  \; .
  \end{split}
\end{equation}
It is immediate to see that the basis tau functions correspond to
Slavnov products for the case \(n=2\). We also take the limit \(z_1\to
w\); then
\begin{equation}
  \bm{\tau}(w; v_1 , v_2, v_3) = 
  \frac{1}{(w - v_1)(w - v_2)(w - v_3)} \mathcal{W}[\mathcal{Y}_1, \mathcal{Y}_2, \mathcal{Y}_3](w)\; .
\end{equation}

Of course, we could continue the calculations for other cases, but it
is now clear that this explicit analysis becomes cumbersome quite
quickly. This also explains why we restrict our analysis to the
rational cases.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Baker-Akhiezer function}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

This section addresses some properties of the Baker-Akhiezer functions
associated with the tau functions derived above. While many aspects of
these functions deserve thorough examination, here we focus on their
most essential properties.

@@

We now aim to express the Slavnov products defined above in terms of
the following coordinates
\begin{equation}
  t_p = \frac{1}{p}\sum_{j=1}^n z_j^p\; ,
\end{equation}
the so-called Miwa coordinates. Let us also define the function
\begin{equation}
  \xi(\bm{t}, \lambda) = \sum_{p=1}^\infty t_p \lambda^p\; , 
\end{equation}
where \(\lambda\) is a complex parameter.

Therefore
\begin{equation}
  \begin{split}
    e^{\xi(\bm{t}, \lambda)} & = \exp\left( \sum_{p=1}^\infty t_p \lambda^p \right)
    = \exp\left( \sum_{p=1}^\infty \sum_{j=1}^n \frac{1}{p} z^p \lambda^p \right) \\
    & = \exp\left( \sum_{j=1}^n \sum_{p=1}^\infty  \frac{1}{p} z_j^p \lambda^p \right)
    = \exp\left( - \sum_{j=1}^n \ln( 1 -  z_j \lambda ) \right) \\
    & =  \prod_{j=1}^n \frac{1}{1 -  z_j \lambda} \; .
  \end{split}
\end{equation}
It is easy to see that these functions have simple poles at \( \lambda = z_j^{-1}\).

\begin{proposition}
It has been established that tau functions in the alternant
form~(\ref{eq:slav-tau-function}) admits the following integral
representation
\begin{subequations}
\begin{equation}
  \label{eq:tau-function-miwa}
  \bm{\tau}(\bm{t}, \bm{v}) =
    \det_{j,k}\left(
    \oint_{\gamma_k} \frac{d w}{2\pi i} e^{\xi(\bm{t}, w^{-1})} \frac{w^{-j}\mathcal{Y}_k(w)}{w - v_k} \right)\; ,
\end{equation}
where 
\begin{equation}
  \xi(\bm{t}, w^{-1}) = \sum_{p=1}^\infty t_p w^{-p} \quad \Leftrightarrow \quad
  \xi(\bm{z}, w^{-1}) = w^n \prod_{j=1}^n (w - z_j)^{-1} \; . 
\end{equation}
In the above integral, we consider that integration curve \(\gamma_k\)
encloses all poles except the Bethe root \(v_k\).
\end{subequations}
\end{proposition}

\paragraph{\textbf{\emph{Proof}}}

As far as we know, this result was first established
in~\cite{ZinnJustin:2002cr, ZinnJustin:2002pk}; see
also~\cite{Zinnjustin2009, Araujo:2021ghu} for further
discussions. Here, we present a proof of this result for pedagogical
reasons and to address some differences that arise due to our
conventions.
\todo{21/05}

In terms of the \(z\)-coordinates, the tau functions becomes
\begin{equation}
  \label{eq:tau-function}
  \bm{\tau}(\bm{z}, \bm{v}) =
    \det_{j,k}\left(
    \oint_{\gamma_k} \frac{d w}{2\pi i}
    \prod_{l=1}^n \frac{1}{w - z_l} \frac{w^{n-j}\mathcal{Y}_k(w)}{w - v_k} \right) \; . 
\end{equation}
Now, it is easy to see that \(w =0\) is not a pole.  All in all, the
integration curve \(\gamma_k\) encloses points \(\{z_j\}_{j=1}^n\).
